CommonMind Consortium: DLPFC

### 2020-09-21 combined_analysis/diff.networks.Rmd
Update diff networks

	# Discover clusters in first cohort
	#----------------------------------
	C.diff.discovery = diff.net[[1]][keep.ensID,keep.ensID]

@@

# Null permuations
```{r diff.networks.null}

@@

```{r recalibrate.null}

df_test_recal = apply_permutation_null( df_test_null )

@@

```

@@

# Discover clusters in first cohort
#----------------------------------
C.diff.discovery = diff.net.Sex[[1]][keep.ensID,keep.ensID]

@@

@@

i = which(df_cohort2$FDR < 0.05)

@@

@@

@@

i = which(df_cohort2$FDR < 0.1)

>>>>

	# Discover clusters in first cohort
	#----------------------------------
	C = diff.net[[1]]
	C.diff.discovery = C[[2]] - C[[1]]
	C.diff.discovery = C.diff.discovery[[1]][keep.ensID,keep.ensID]

@@

# Null network
```{r diff.networks.null}

@@

```{r recalibrate.null}
df_test_recal = apply_permutation_null( df_test_null )

table(df_test_recal$FDR < 0.05)

@@

table(df_test_meta$FDR < 0.05)
```

@@

res = pickSFT( diff.net.Sex )

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab(="Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

# Discover clusters in first cohort
#----------------------------------
C = diff.net[[1]]
C.diff.discovery = C[[2]] - C[[1]]
C.diff.discovery = C.diff.discovery[[1]][keep.ensID,keep.ensID]

@@

df_sft = pickSFT( diff.net.Sex )

```{r recalibrate.Sex}
table(df_test.Sex$FDR < 0.05)

df_test_recal = apply_permutation_null( df_test.Sex )

table(df_test_recal$FDR < 0.05)

df_test_meta = module_meta_analysis( df_test_recal )

table(df_test_meta$FDR < 0.05)
```

@@

# i = which(df_cohort2$FDR < 0.05)
i = 1:5

@@

```{r recalibrate.Dx}
table(df_test.Dx$FDR < 0.05)

df_test_recal = apply_permutation_null( df_test.Dx )

table(df_test_recal$FDR < 0.05)

df_test_meta = module_meta_analysis( df_test_recal )

table(df_test_meta$FDR < 0.05)
```

@@

```{r recalibrate.Dx_Sex}
table(df_test.Dx_Sex$FDR < 0.05)

df_test_recal = apply_permutation_null( df_test.Dx_Sex )

table(df_test_recal$FDR < 0.05)

df_test_meta = module_meta_analysis( df_test_recal )

table(df_test_meta$FDR < 0.051)
```

@@

# i = which(df_cohort2$FDR < 0.1) 
i = 1:5
